\item \link{https://daniel-halpern.com}{D. Halpern}, \link{https://safwanhossain.github.io}{S. Hossain}, and \link{http://www.jamie.tuckerfoltz.com}{J. Tucker-Foltz}. \websitelink{social-choice-queries}{Computing Voting Rules with Elicited Incomplete Votes}. In \textit{Proceedings of the 25th ACM Conference on Economics and Computation (\textbf{EC})}, 2024. Forthcoming.

\item \link{http://www.gerdusbenade.com}{G. Benadè}, \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.alexpsomas.com}{A. Psomas}, and \link{https://sites.google.com/view/paritoshverma/}{P. Verma}. \websitelink{ef-beyond-additive}{On the Existence of Envy-Free Allocations Beyond Additive Valuations}. In \textit{Proceedings of the 25th ACM Conference on Economics and Computation (\textbf{EC})}, 2024. Forthcoming.

\item \link{https://ebadian.org}{S. Ebadian}, \link{https://daniel-halpern.com}{D. Halpern}, and \link{https://www.cs.toronto.edu/~emicha/}{E. Micha}. \websitelink{metric-distortion-with-queries}{Metric Distortion with Elicited Pairwise Comparisons}. In \textit{Proceedings of the 33rd International Joint Conference on Artificial Intelligence (\textbf{IJCAI})}, pp. 2791--2798, 2024.

\item \link{https://www.mpib-berlin.mpg.de/staff/fabian-baumann}{F. Baumman}, \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.rahwan.me}{I. Rahwan}, \link{https://seas.harvard.edu/person/itai-shapira}{I. Shapira}, \link{http://procaccia.info}{A. D. Procaccia}, and \link{https://ei.is.mpg.de/~mwuthrich}{M. Wüthrich}. \websitelink{twitter}{Optimal Engagement-Diversity Tradeoffs in Social Media}. In \textit{Proceedings of the 33rd ACM Web Conference (\textbf{WWW})}, pp. 288--299, 2024.

\item \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.linkedin.com/in/rachelxli/}{R. Li}, and \link{http://procaccia.info}{A. D. Procaccia}. \websitelink{strategy-proof-beliefs}{Strategyproof Voting under Correlated Beliefs}. In \textit{Proceedings of the 37th Conference on Neural Information Processing Systems (\textbf{NeurIPS})}, pp. 39744--39754, 2023.

\item \link{https://sites.google.com/andrew.cmu.edu/baileyflanigan/home}{B. Flanigan}, \link{https://daniel-halpern.com}{D. Halpern}, and \link{https://www.alexpsomas.com}{A. Psomas}. \websitelink{smoothed-analysis}{Smoothed Analysis of Social Choice Revisited}. In \textit{Proceedings of the 19th Conference on Web and Internet Economics (\textbf{WINE})}, pp. 290--309, 2023.

\item \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.cs.cornell.edu/home/halpern/}{J. Y. Halpern}, \link{https://jadbabaie.mit.edu}{A. Jadbabaie}, \link{https://math.mit.edu/~elmos/}{E. Mossel}, \link{http://procaccia.info}{A. D. Procaccia}, and \link{https://manrev.github.io/manon/}{M. Revel}. \websitelink{liquid-defense}{In Defense of Liquid Democracy}. In \textit{Proceedings of the 24th ACM Conference on Economics and Computation (\textbf{EC})}, pp. 852, 2023.

\item \link{https://daniel-halpern.com}{D. Halpern}, \link{https://gregorykehne.com}{G. Kehne}, \link{http://procaccia.info}{A. D. Procaccia}, \link{http://www.jamie.tuckerfoltz.com}{J. Tucker-Foltz}, and \link{https://ei.is.mpg.de/~mwuthrich}{M. Wüthrich}. \websitelink{representation-incomplete}{Representation with Incomplete Votes}. In \textit{Proceedings of the 37th AAAI Conference on Artificial Intelligence (\textbf{AAAI})}, pp. 5657--5664, 2023.

\item \link{http://www.gerdusbenade.com}{G. Benadè}, \link{https://daniel-halpern.com}{D. Halpern}, and \link{https://www.alexpsomas.com}{A. Psomas}. \websitelink{dynamic-fair-division}{Dynamic Fair Division with Partial Information}. In \textit{Proceedings of the 36th Conference on Neural Information Processing Systems (\textbf{NeurIPS})}, pp. 3703--3715, 2022.

\item \link{https://manrev.github.io/manon/}{M. Revel}, \link{https://daniel-halpern.com}{D. Halpern}, \link{https://polisci.mit.edu/people/adam-berinsky}{A. Berinsky}, and \link{https://jadbabaie.mit.edu}{A. Jadbabaie}. \websitelink{liquid-in-practice}{Liquid Democracy in Practice: An Empirical Analysis of its Epistemic Performance}. In \textit{Proceedings of the 2nd ACM conference on Equity and Access in Algorithms, Mechanisms, Optimization (\textbf{EAAMO})}, 2022.

\item \link{https://www.cs.toronto.edu/~bor/}{A. Borodin}, \link{https://daniel-halpern.com}{D. Halpern}, \link{https://www.cs.toronto.edu/~latifian/}{M. Latifian}, and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \websitelink{distortion-top-t}{Distortion in Voting with Top-t Preferences}. In \textit{Proceedings of the 31st International Joint Conference on Artificial Intelligence (\textbf{IJCAI})}, pp. 116--122, 2022.

\item \link{https://daniel-halpern.com}{D. Halpern}, \link{https://gregorykehne.com}{G. Kehne}, and \link{http://www.jamie.tuckerfoltz.com}{J. Tucker-Foltz}. \websitelink{buyers-reveal}{Can Buyers Reveal for a Better Deal?}. In \textit{Proceedings of the 31st International Joint Conference on Artificial Intelligence (\textbf{IJCAI})}, pp. 314--320, 2022.

\item \link{https://manrev.github.io/manon/}{M. Revel}, \link{https://tao-l.github.io}{T. Lin}, and \link{https://daniel-halpern.com}{D. Halpern}. \websitelink{optimal-congress}{How Many Representatives Do We Need? The Optimal Size of an Epistemic Congress}. In \textit{Proceedings of the 36th AAAI Conference on Artificial Intelligence (\textbf{AAAI})}, pp. 9431--9438, 2022.

\item \link{https://daniel-halpern.com}{D. Halpern} and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \websitelink{distortion-fair-division}{Fair and Efficient Resource Allocation with Partial Information}. In \textit{Proceedings of the 30th International Joint Conference on Artificial Intelligence (\textbf{IJCAI})}, pp. 224--230, 2021.

\item \link{https://daniel-halpern.com}{D. Halpern}, \link{https://gregorykehne.com}{G. Kehne}, \link{https://dominik-peters.de}{D. Peters}, \link{http://procaccia.info}{A. D. Procaccia}, \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}, and \link{https://www.mimuw.edu.pl/~ps219737/}{P. Skowron}. \websitelink{ranked-binary-judgments}{Aggregating Binary Judgments Ranked By Accuracy}. In \textit{Proceedings of the 35th AAAI Conference on Artificial Intelligence (\textbf{AAAI})}, pp. 5456--5463, 2021.

\item \link{https://daniel-halpern.com}{D. Halpern}, \link{http://procaccia.info}{A. D. Procaccia}, \link{https://www.alexpsomas.com}{A. Psomas}, and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \websitelink{binary-mnw}{Fair Division with Binary Valuations: One Rule to Rule Them All}. In \textit{Proceedings of the 16th Conference on Web and Internet Economics (\textbf{WINE})}, pp. 370--383, 2020.

\item \link{https://www.cs.drexel.edu/~gkatz/}{V. Gkatzelis}, \link{https://daniel-halpern.com}{D. Halpern}, and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \websitelink{optimal-metric-distortion}{Resolving the Optimal Metric Distortion Conjecture}. In \textit{Proceedings of the 61st Annual IEEE Symposium on Foundations of Computer Science (\textbf{FOCS})}, pp. 1427--1438, 2020.

\item \link{https://daniel-halpern.com}{D. Halpern} and \link{https://www.cs.toronto.edu/~nisarg}{N. Shah}. \websitelink{fair-division-subsidy-full}{Fair Division with Subsidy}. In \textit{Proceedings of the 12th International Symposium on Algorithmic Game Theory (\textbf{SAGT})}, pp. 374--389, 2019.

