\documentclass{article}
\usepackage{scimisc-cv}
\usepackage[hidelinks]{hyperref}
\usepackage{etoolbox}
%\usepackage{etaremune}
\usepackage{xspace}

\title{Daniel Halpern's Resume}
\author{Daniel Halpern}
\date{\today}

\providetoggle{uselinks}
\settoggle{uselinks}{true}
\newcommand{\link}[2]{\iftoggle{uselinks}{\href{#1}{#2}}{#2}\xspace}
\newcommand{\itlink}[2]{\link{https://daniel-halpern.com/files/#1.pdf}{\textit{#2}}}

\newcommand{\me}{\link{https://daniel-halpern.com}{D. Halpern}}
\newcommand{\nisarg}{\link{https://www.cs.toronto.edu/~nisarg}{N. Shah}}
\newcommand{\vasilis}{\link{https://www.cs.drexel.edu/~gkatz/}{V. Gkatzelis}}
\newcommand{\ariel}{\link{http://procaccia.info}{A. D. Procaccia}}
\newcommand{\alex}{\link{https://www.alexpsomas.com}{A. Psomas}}
\newcommand{\greg}{\link{https://gregorykehne.com}{G. Kehne}}
\newcommand{\dominik}{\link{https://dominik-peters.de}{D. Peters}}
\newcommand{\piotr}{\link{https://www.mimuw.edu.pl/~ps219737/}{P. Skowron}}
\newcommand{\manon}{\link{https://manrev.github.io/manon/}{M. Revel}}
\newcommand{\tao}{\link{https://tao-l.github.io}{T. Lin}}
\newcommand{\jamie}{\link{http://www.jamie.tuckerfoltz.com}{J. Tucker-Foltz}}
\newcommand{\dad}{\link{https://www.cs.cornell.edu/home/halpern/}{J. Y. Halpern}}
\newcommand{\ali}{\link{https://jadbabaie.mit.edu}{A. Jadbabaie}}
\newcommand{\elchanan}{\link{https://math.mit.edu/~elmos/}{E. Mossel}}
\newcommand{\allan}{\link{https://www.cs.toronto.edu/~bor/}{A. Borodin}}
\newcommand{\mohamad}{\link{https://www.cs.toronto.edu/~latifian/}{M. Latifian}}
\newcommand{\bailey}{\link{https://sites.google.com/andrew.cmu.edu/baileyflanigan/home}{B. Flanigan}}
\newcommand{\adam}{\link{https://polisci.mit.edu/people/adam-berinsky}{A. Berinsky}}


%% These are custom commands defined in scimisc-cv.sty
\cvname{Daniel Halpern}
\cvpersonalinfo{
\link{https://goo.gl/maps/UNphRr9rd6dAY47B7}{150 Western Ave, Allston, MA, 02134} \cvinfosep
\link{tel:16072274045}{+1 (607) 227--4045} \cvinfosep
\link{mailto:dhalpern@g.harvard.edu}{dhalpern@g.harvard.edu} \cvinfosep
\link{https://daniel-halpern.com}{https://daniel-halpern.com}
}



\begin{document}


% \maketitle %% This is LaTeX's default title constructed from \title,\author,\date

    \makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo

    \section{Education}

    \cvsubsection{Harvard University}[Cambridge, MA]
    [Ph.D. in Computer Science][August 2020 to present]
    \begin{itemize}
        \item Advisor: \link{http://procaccia.info}{Ariel Procaccia}
    \end{itemize}

    \cvsubsection{University of Toronto}[Toronto, ON]
    [B.Sc. in Computer Science with High Distinction][September 2016 to June 2020]
    \begin{itemize}
        \item Major GPA: 4.0/4.0, Cumulative GPA: 3.96/4.0
    \end{itemize}


    \section{Work Experience}
    \cvsubsection{Carnegie Mellon University}[Pittsburgh, PA]
    [Research Intern][June 2019 - August 2019]
    \begin{itemize}[noitemsep,nolistsep]
        \item Worked with Professor Ariel Procaccia
        \item Research in topics related to Algorithmic Game Theory
    \end{itemize}

    \cvsubsection{CryptoNumerics}[Toronto, ON]
    [Software Developer][April 2018 - July 2020]
    \begin{itemize}[noitemsep,nolistsep]
        \item One of the first employees at start up working on machine learning and cryptography
        \item Leader of several projects in Python, Java, and Javascript
    \end{itemize}


%    \section{Teaching Experience}
%    \cvsubsection{University of Toronto}[Toronto, ON]
%    [Undergraduate Teaching Assistant][Spring 2020]
%    \begin{itemize}
%        \item Data Structures and Analysis (CSC263)
%    \end{itemize}
%
%    \cvsubsection{University of Toronto}[Toronto, ON]
%    [Undergraduate Teaching Assistant][Spring 2020]
%    \begin{itemize}
%        \item Algorithm Design, Analysis \& Complexity (CSC373)
%    \end{itemize}


    \section{Awards}
    \begin{itemize}
     \setlength\itemsep{.8ex}
    	\item \textbf{\textsl{National Science Foundation Graduate Research Fellowship}}\hfill 2021
        \item \textsl{University of Toronto Computer Science Undergraduate Research Award} \hfill 2020
%        \$6000 award for undergraduate summer research
        \item \textsl{Harold Willet Stewart Memorial Scholarship} \hfill 2020
%        \$2080 graduating year award
        \item \textsl{Anna And Alex Beverly Memorial Fellowship} \hfill 2020
%        \$1000 graduating year award
        \item \textsl{Samuel Beatty In Course Scholarship} \hfill 2019
%        \$1500 given for academic achievement
        \item \textsl{C. L. Burton Scholarship For Mathematics and Physical Sciences} \hfill 2019
%        \$500 given for academic achievement
        \item \textsl{Dr. James A. \& Connie P. Dickson Scholarship in Science \& Mathematics} \hfill 2018
%        \$500 given for academic achievement
        \item \textsl{Alan Milne McCombie Scholarship} \hfill 2017
%        \$250 given for academic achievement
        \item \textsl{University of Toronto President's Scholars of Excellence Program} \hfill 2016
%        \$10,000 incoming student scholarship
    \end{itemize}


    \section{Publications}
    \begin{itemize}
        \setlength\itemsep{.8ex}
        \item \manon, \me, \adam, and \ali. \itlink{liquid-in-practice}{Liquid Democracy in Practice: An Empirical Analysis of its Epistemic Performance}. Working Paper.
        \item \me, \dad, \ali, \elchanan, \ariel, and \manon. \itlink{liquid-defense}{In Defense of Fluid Democracy}. Working Paper.

        \item \me and \ariel. \itlink{unbiased-information}{Unbiased Information Packets}. Working Paper.

        \item \allan, \me, \mohamad, and \nisarg. \itlink{distortion-top-t}{Distortion in Voting with Top-t Preferences}. Proc. of 31st International Joint Conference on Artificial Intelligence (\textbf{IJCAI}), 2022. Forthcoming.
        
        \item \me, \greg, and \jamie. \itlink{buyers-reveal}{Can Buyers Reveal for a Better Deal?}. Proc. of 31st International Joint Conference on Artificial Intelligence (\textbf{IJCAI}), 2022. Forthcoming.
        
        \item \manon, \tao, and \me. \itlink{optimal-congress}{How Many Representatives Do We Need? The Optimal Size of an Epistemic Congress}.
        Proc. of 36th AAAI Conference on Artificial Intelligence (\textbf{AAAI}), 2022. Forthcoming. 
        
        \item \me and \nisarg \itlink{distortion-fair-division}{Fair and Efficient Resource Allocation with Partial Information}.
        Proc. of 30th International Joint Conference on Artificial Intelligence (\textbf{IJCAI}), pp. 224-230, 2021. 
        
        \item \me, \greg, \dominik, \ariel, \nisarg, and \piotr. \itlink{ranked-binary-judgments}{Aggregating Binary Judgments Ranked By Accuracy}.
        Proc. of 35th AAAI Conference on Artificial Intelligence (\textbf{AAAI}), pp. 5456-5463, 2021. 

        \item \me, \ariel, \alex, and \nisarg. \itlink{binary-mnw}{Fair Division with Binary Valuations: One
        Rule to Rule
        Them All}. Proc. of 16th Conference on Web and Internet Economics (\textbf{WINE}), pp. 370-383, 2020.
        
        \item \vasilis, \me, and \nisarg. \itlink{optimal-metric-distortion}{Resolving the Optimal Metric Distortion Conjecture}.
        Proc. of 61st Annual IEEE Symposium on Foundations of Computer Science (\textbf{FOCS}), pp. 1427-1438, 2020.

        \item \me and \nisarg. \itlink{fair-division-subsidy-full}{Fair Division with Subsidy}. Proceedings of the 12th International Symposium on
        Algorithmic Game Theory (\textbf{SAGT}), pp. 374-389, 2019.

    \end{itemize}


\end{document}
